---
title: "ModelEvaluation_Dataset Jumlah Siswa dan Guru DKI Jakarta 2018"
output: html_document
---


```{r}
Data <- read.csv(file="data jumlah siswa dan guru sma jkt 2018.csv", header = TRUE)
Data
nrow(Data)
```

```{r}
library(caret)
set.seed(1)

#splitting data into training and test sets
trainIndex <- createDataPartition(Data$guru, p = 0.6)$Resample1

trainingSet <- Data[trainIndex, ]
testingSet <- Data[-trainIndex, ]

trainingSet
testingSet
```


```{r load_data, results="hide", attr.source = ".numberLines"}
Data <- read.csv(file="data jumlah siswa dan guru sma jkt 2018.csv", header = TRUE)
summary(Data)
```


#Confussion Matrix
#It take a 'few' minutes
```{r}
library(caret)
train_control <- trainControl(method="cv", number=10)

modelNB <- train(status ~ npsn + guru, method = "nb", trControl = train_control, data = Data)

modelNB$resample
confusionMatrix(modelNB)
```


#It take a 'few' minutes
``````{r repeated, results="hide", warning = FALSE, message=FALSE, attr.source = ".numberLines"}
train_control <- trainControl(method="repeatedcv", number=10, repeats=5)

modelNB <- train(status ~ npsn + guru, method = "nb", trControl = train_control, data = Data)

modelNB$resample
confusionMatrix(modelNB)
```


# Leave-One-Out cross validation (LOOCV)
#It take a 'few' minutes
```{r loov, warning = FALSE, message=FALSE, attr.source = ".numberLines", results="hide"}
train_control <- trainControl(method="LOOCV")

modelNB <- train(status ~ npsn + guru, method = "nb", trControl = train_control, data = Data)

modelNB$results
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

