---
title: "SVM_Random Dataset"
output: html_document
---



```{r}
set.seed(339933)
```



```{r}
x <-  matrix(rnorm(100), 20, 2)
x
```



```{r}
y <-  factor(rep(c(-1, 1), c(10, 10)))
y
```



```{r}
x[y == 1, ] <- x[y == 1, ] + 3
x
```
```{r}
Data <- data.frame(x,y)
head(Data)
```



``````{r, generate data}
colnames(Data) <- c("Prtmna", "Shll", "qlty")
head(Data)
```



```{r}
plot(Data$Prtmna,Data$Shll, col = ifelse(y=="1", "blue", "red"), pch = 20)
```



```{r}
library(e1071)
```



```{r, svmVis, warning = FALSE,message=FALSE}
modelSVM1 <- svm(qlty ~ ., data = Data, kernel = "linear")
```



```{r}
print(modelSVM1)
```



```{r, plotSVM}
plot(modelSVM1, Data)
```



```{r}
library(caret)
```



```{r}
set.seed(123)
```



```{r}
train_control <- trainControl(method="cv", number=5)
```



```{r}
modelSVM2 <- train(qlty ~., data = Data, method = "svmLinear", trControl = train_control)
```



```{r, svmCrossVal, warning=FALSE, message=FALSE}
modelSVM2$resample
```



```{r, svmCrossVal2}
confusionMatrix(modelSVM2)
```



```{r}
set.seed(134)
```



```{r}
n <- 1500
```



```{r}
x <- cbind(runif(n),runif(n))
```



```{r}
eta  <- x[,2] - sin(10*x[,1])
prob <- 1/(1+exp(-5*eta))
y    <- 2*rbinom(n, 1, prob)-1
y  <- as.factor(y)
```



```{r}
Data2 <- data.frame(x,y)
```



```{r}
colnames(Data2) <- c("Prtmna", "Shll", "qlty")
head(Data2)
```



```{r}
plot(Data2$Prtmna,Data2$Shll, col = ifelse(y=="1", "blue", "red"), pch = 20)
legend("topright", c("Y=1","Y=-1"),pch=20,col=c("blue", "red"), inset=0.05, bg=gray(1), cex=1.5)
``` 



```{r}
library(e1071)
# set.seed(330)
modelSVM3 <-  svm(qlty ~ ., data = Data2, kernel = "radial")
print(modelSVM3)
```



```{r}
plot(modelSVM3, Data2)
```



```{r}
library(caret)
set.seed(339)
train_control2 <- trainControl(method="cv", number=10)
modelSVM4 <- train(qlty ~., data = Data2, method = "svmRadial", trControl = train_control2)
modelSVM4$resample
```



```{r}
confusionMatrix(modelSVM4)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

